Adolescent well-being in the digital age

### 2022-05-06 00-clean.Rmd
Missed one!
Update ITU data and fix typo

@@

# Download data sets from the ITU website if not yet downloaded
if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
  dir.create("data-raw/ITU")
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/PercentIndividualsUsingInternet_Nov2021.xlsx",
    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx",
    "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx",
    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
  )
}

@@

# Centering predictors within and between countries
itu <- itu %>%
  group_by(country) %>%
  mutate(
    # Year-specific deviations from country average
    i_cw = internet - mean(internet, na.rm = TRUE), 
    m_cw = internet - mean(mobile, na.rm = TRUE),
    h_cw = internet - mean(hdi, na.rm = TRUE),
    i1_cw = i1 - mean(i1, na.rm = TRUE), 
    m1_cw = m1 - mean(m1, na.rm = TRUE),
    h1_cw = h1 - mean(h1, na.rm = TRUE)
  ) %>% 
  ungroup()

@@

# Arrange on outcome
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
dat <- dat %>%
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  arrange(outcome, region, country, year)

>>>>

# Common options
source("_common.R")

@@

# Download data sets from the ITU website if not yet downloaded
if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
  dir.create("data-raw/ITU")
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/PercentIndividualsUsingInternet.xlsx",
    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/FixedBroadbandSubscriptions_2000-2020.xlsx",
    "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/MobileBroadbandSubscriptions_2007-2020.xlsx",
    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
  )
}

@@

# Centering predictors within and between countries
itu <- itu %>%
  # Grand mean centering so both components are zero-centered
  mutate(across(c(i1, m1, h1), ~. - mean(., na.rm = TRUE))) %>% 
  group_by(country) %>%
  mutate(
    # Between
    i1_cb = mean(i1, na.rm = TRUE),
    m1_cb = mean(m1, na.rm = TRUE),
    h1_cb = mean(h1, na.rm = TRUE),
    # Within
    i1_cw = i1 - i1_cb, 
    m1_cw = m1 - m1_cb,
    h1_cw = h1 - h1_cb
  ) %>% 
  ungroup()

@@

# Arrange on outcome
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
dat <- dat %>%
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  arrange(outcome, country, region, year)
